A Switching Planner for Combined Task and Observation Planning

### 2011-04-26 subarchitectures/planner.sa/trunk/src/latex/AAAI11/aaai11.tex
Some latex-fixes Reduce fontsize of bibliography

\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{graphicx}
\graphicspath{{plots/}}
\include{macros}%

\nocopyright

\pdfinfo{
/Title (A Switching Planner for Combined Task and Observation Planning)
% /Subject (Proceedings of the 21st International Conference on Automated Planning and Scheduling)
/Author (NA)}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
%% \title{Interleaved Serial and Decision-Theoretic Planning for a Mobile Robot}

@@

\title{A Switching Planner for Combined Task and Observation Planning}
\author{anonymous}
\setcounter{secnumdepth}{0}

@@

%% \section{Discussion}
%% \input{discussion.tex}

@@

>>>>

\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{graphicx}
\usepackage{tabularx}
\graphicspath{{plots/}}
\include{macros}%

%%\nocopyright

\special{! /pdfmark where
{pop} {userdict /pdfmark /cleartomark load put} ifelse
[ /Author (Moritz Goebelbecker, Charles O. Gretton, Richard Dearden)
/Title (A Switching Planner for Combined Task and Observation Planning)
/Subject (Proceedings of the Twenty-Fifth Conference on Artificial Intelligence)
/Keywords (planning under uncertainty)
/DOCINFO pdfmark
userdict /pdfmark /cleartomark load put}

\pdfinfo{
/Title (A Switching Planner for Combined Task and Observation Planning)
/Subject (Proceedings of the Twenty-Fifth Conference on Artificial Intelligence)
/Author (Moritz Goebelbecker, Charles O. Gretton, Richard Dearden)
}

% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
%% \title{Interleaved Serial and Decision-Theoretic Planning for a Mobile Robot}

@@

\title{A Switching Planner for Combined Task and Observation Planning}
\author{
Moritz G{\"o}belbecker \\ Albert-Ludwigs-Universit{\"a}t Freiburg, Germany\\
goebelbe@informatik.uni-freiburg.de
\And
Charles O. Gretton, Richard Dearden,\\
University of Birmingham, United Kingdom\\
\{c.gretton,R.W.Dearden\}@cs.bham.ac.uk} 
\setcounter{secnumdepth}{0}

@@

%% \section{Discussion}
%% \noinput{discussion.tex}

@@

\small
\paragraph{Acknowledgements:} The research leading to these results has
received funding from the European Community's Seventh Framework
Programme [FP7/2007-2013] under grant agreement No. 215181, CogX.
